\section{Education}
\vspace{5pt}
\subsection{Academic Qualifications}
\vspace{5pt}
\begin{itemize}
    
    \item{\cventry{2011--2015}{Meng (Hons) Electrical and Electronic Engineering }{Lancaster University}{Lancaster}{\textit{Predicted First Class}}{}}
    
    \item{\cventry{2009--2011}{A levels}{Runshaw College}{Leyland}{\textit{ICT (A) Physics (B) Maths (B)}}{}}  % arguments 3 to 6 can be left empty
    
    \item{\cventry{2002--2009}{11 GCSEs}{Southlands High School}{Chorley}{\textit{A* to B Including Maths and English}}{}}
    
\end{itemize}

\vspace{2pt}
\subsection{Notable Projects}
\vspace{5pt}
\begin{itemize}
    
    \item{\textbf{Masters Project (Ongoing):} \textit{'Development of an Intelligent Humanoid Robot'}
          
          \vspace{3pt}
          
          \small{I am part of a team developing a 5ft autonomous humanoid robot. This ambitious project requires strong team-working skills and high technical ability. I work well as part of the team, contributing in group discussions and taking initiative to set myself tasks when the next stage of the project is not clear. Given the role of electronics supervisor I am responsible for setting goals and ensuring all the electronic system designs are realised on time and meet the specifications of the project.}}
    
    \newpage
    
    \item{\textbf{3rd year individual project:} \textit{'Artificial Neural Network Approach to Source Localisation in Radiation Portal Monitoring'}
          
          \vspace{3pt}
          
          \small{This challenging project took place over the entirety of my third year. It required excellent planning and organisational skills, and the ability to teach myself an entirely new and complex subject. The project was a success, with the system being able to localise a radioactive source down to $ 3 cm$ within a $ 600 m^3$ sensor array. This project has been suggested for publication by my supervisor.}}
    
    \vspace{6pt}
    
    \item{\textbf{Industrial Project with Leyland Motors Ltd:}\textit{'Development of a Facility to Ensure the Achievement of Torque Parameters for a Specific Axle Configuration'}
          
          \vspace{3pt}
          
          \small{In the 3rd year of my course I spent a week completing an industrial project for Leyland Motors. I worked with a team operating as consultants for a particular problem the company was having. During this project I was working in a professional environment, and co-operating with various managers and engineers to create a design that met the requirements of the problem.}}
    
\end{itemize}