\section{Work Experience}
\subsection{Professional}
\vspace{5pt}
\begin{itemize}
    \item{\cventry{May 2017--Jul 2017}{Software Engineering Intern}{The Ramco Cements Ltd}{Jaggayapeta, India}{}{\vspace{3pt} Designed a petrol bunk inventory management system using Angular.js. Implemented a relational database model for the same using SQLite. The back-end infrastructure was written in Python using Flask.}}
    \vspace{5pt}
    
    \item{\cventry{May 2018 – Jul 2018}{Software Engineering Intern}{Apras Polymers \& Engineering Co.Pvt. Ltd}{Nashik, India}{}{\vspace{3pt} Designed a responsive website for the company using Figma. Implemented the front end using React.js, Jekyll and Bootstrap.}}
    \vspace{5pt}
    

\end{itemize}
\subsection{Academic}
\vspace{5pt}
    \begin{itemize}
        \item{\cventry{Dec 2018 - May 2019}{Undergraduate Research Assistant}{CSIR-Central Electronics Engineering Research Institute, Pilani}{Pilani, India}{}{\vspace{3pt} Researched convolutional neural network models for orientation-aware object detection on aerial images. Achieved approximately 65 mAP on the DOTA dataset.}}
        
        \vspace{5pt}
                
        \item{\cventry{Jul 2018 - Dec 2018}{Undergraduate Research Intern}{CSIR-Central Electronics Engineering Research Institute, Pilani}{Pilani, India}{}{\vspace{3pt} Worked on designing instance segmentation models for real-time power-cable fault detection using autonomous drones under Dr. Sumeet Saurav}}
    
        \vspace{5pt}
        
        \item{\cventry{Aug 2017- Dec 2017}{Undergraduate Research Assistant}{BITS Pilani}{Pilani, India}{}{\vspace{3pt} Worked on fault tolerant Static RAM cell design under Prof. Anu Gupta}}
    \end{itemize}